pirouette: Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-03-18 article.tex
Use 'x = x' idiom in all code

\begin{lstlisting}[language=R, floatplacement=ht, frame=single]
errors <- pir_run(
  phylogeny,
  pir_params = pir_params
)
pir_plot(errors)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, floatplacement=ht, frame=single]
errors <- pir_run(
  phylogeny,
  pir_params = pir_params
)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, floatplacement=H, frame=single]
errors <- pir_run(
  phylogeny,
  pir_params = pir_params
)
\end{lstlisting}

>>>>

\begin{lstlisting}[language=R, floatplacement=ht, frame=single]
errors <- pir_run(
  phylogeny = phylogeny,
  pir_params = pir_params
)
pir_plot(errors)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, floatplacement=ht, frame=single]
errors <- pir_run(
  phylogeny = phylogeny,
  pir_params = pir_params
)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, floatplacement=H, frame=single]
errors <- pir_run(
  phylogeny = phylogeny,
  pir_params = pir_params
)
\end{lstlisting}
